Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming

### 2020-09-08 Paper/manuscript_v2/manuscript_07_02.tex
add diagnosis example for case study I (2)

>>>>

{\color{black!75}
In practice, as the high computational demands of exact GPs prevents their use to asses the performance of the approximation, the diagnosis of the approximation as a function of $m$ and $c$ as proposed in Section \ref{ch5_subsec_dependency} is recommended. 
%The diagnosis consists in comparing the estimated length-scale $\hat{\ell}$ for a given $m$ and $c$, with that minimum length-scale $\ell^*$ that can be accurately approximated, for those given $m$ and $c$, generated by the model of relationships in Figures \ref{fig6_lscale_vs_J_vs_c} and \ref{fig6_lscale_vs_J_vs_c_Matern}. Thus, if $\hat{\ell} < \ell^*$, $m$ needs to increased or $c$ decreased, and this can be iteratively until we get $\hat{\ell} \geq \ell^*$. 
Figure \ref{ch5_fig12_diagnosis} depicts the diagnosis applied for the this case study. In a first iteration, the HSGP is launched with $m=20$ and $c=1.5$, which is not a valid combination of $m$ and $c$, as $c=1.5$ is too small for $m=20$ or $m=20$ is too small for $c=1.5$, as can be seen in the corresponding plot of Figure \ref{ch5_fig12_diagnosis}. In a second iteration, we increase $m$ up to $m=30$ and the HSGP estimates a length-scale of $\hat{\ell}=0.12$; and the minimum length-scale that can be accurately approximated, for those $m$ and $c$, generated by the model of relationships in Figure \ref{fig6_lscale_vs_J_vs_c_Matern} is $\ell^*=0.19$. As $\hat{\ell} < \ell^*$, the approximation should not be sufficiently accurate (see Figure \ref{ch5_fig11_MSE_exI_inter}-left where the interpolation error of HSGP is higher than that of GP). In a third iteration, we increase up to $m=40$, the HSGP model estimates a length-scale of $\hat{\ell}=0.14$ and the model of relationships brings a minimum approachable length-scale of $\ell^*=0.15$. As $\hat{\ell}$ is still lower than $\ell^*$, the approximation should not be sufficiently accurate, although, since $\hat{\ell}$ is very closed to $\ell^*$, the approximation might be close to the GP (see errors in Figure \ref{ch5_fig11_MSE_exI_inter}-left). In a fourth iteration, we increase up to $m=60$, the estimated length-scale is $\hat{\ell}=0.14$ and the minimum approachable length-scale generated by the model of relationships is $\ell^*=0.11$, then the approximation should be sufficiently accurate.}

\begin{figure}
\begin{tabular}{cccc}
\hspace{-6mm} {\Large 1}\, \pbox{2cm}{\footnotesize $m=20$\\ $c=1.5$}\! \pbox{1cm}{$\underset{\longrightarrow}{\text{\tiny HSGP}}$\\[-1mm]}\,  {\footnotesize$\hat{\ell}=0.09$} & \hspace{-5mm} {\Large 2}\, \pbox{2cm}{\footnotesize $m=30$\\ $c=1.5$}\! \pbox{1cm}{$\underset{\longrightarrow}{\text{\tiny HSGP}}$\\[-1mm]}\, {\footnotesize$\hat{\ell}=0.12$} & \hspace{-3mm} {\Large 3}\, \pbox{2cm}{\footnotesize $m=40$\\ $c=1.5$}\! \pbox{1cm}{$\underset{\longrightarrow}{\text{\tiny HSGP}}$\\[-1mm]}\, {\footnotesize$\hat{\ell}=0.14$} & \hspace{-3mm} {\Large 4}\, \pbox{2cm}{\footnotesize $m=60$\\ $c=1.5$}\! \pbox{1cm}{$\underset{\longrightarrow}{\text{\tiny HSGP}}$\\[-1mm]}\, {\footnotesize$\hat{\ell}=0.14$} \\[3mm]
	& $\hat{\ell} < \ell^*$ & $\hat{\ell} < \ell^*$ & $\hat{\ell} > \ell^*$\\[1mm]
\hspace{-3mm} \includegraphics[scale=0.22, trim = 0mm 0mm 4mm 10mm, clip]{caseI_fig6_1_1_vposter.pdf} & \hspace{-3mm}
\includegraphics[scale=0.22, trim = 14mm 0mm 4mm 10mm, clip]{caseI_fig6_2_1_vposter.pdf} & \hspace{-3mm}
\includegraphics[scale=0.22, trim = 14mm 0mm 4mm 10mm, clip]{caseI_fig6_3_1_vposter.pdf} & \hspace{-4mm}
\includegraphics[scale=0.22, trim = 14mm 0mm 4mm 10mm, clip]{caseI_fig6_4_1_vposter.pdf} \\[1mm]
\end{tabular}
\caption{Diagnosis of the approximation as a function of the number of basis functions $m$ and boundary factor $c$.}
	\label{ch5_fig12_diagnosis}
\end{figure}
